Title?

### 2018-05-05 paper_wc.tex
Intro and problem (real world application)

\begin{abstract}
We investigate the 2cm app, a data-exchange platform published for China Mobile Hong
Kong 4G Pro Service Plan customers. Telecommunications ISPs' revenue is typically
gained by charging users a fixed fee for a maximum amount
of data usage in a month, i.e., a monthly data cap \cite{???}. 
2cm's (2nd exchange market) data exchange platform allows users to submit
bids to buy and sell data.
This usage model, is, as far as our knowledge, the first data trading
platform that allows customers to buy and sell their own data.
We describe a distributed auction mechanism for data exchange inspired by the
classic PSP throughput problem,
and prove that our distributed data exchange mechanism provides incentive
compatibility (social choice function), and that we have efficiency
using only partial valuation information of each participant in an exchange market.

@@

(NOTE: THE INTRODUCTION IS CURRENTLY A COLLECTION OF NOTES AND PARTIAL
SENTENCES)
In this work, we propose \emph{a distributed progressive second price (PSP) auction in
order to maximize social utility in the CMHK market}. Using the
distributed PSP mechanism on CMHKs data
exhange platform, we show that for cellular data allocated between multiple users there
exists an $\epsilon$-Nash market equilibria. A quality of the PSP auction is that
demand information is not known centrally, rather, it is distributed in the
buyers' valuations. The mechanism for an auction is defined
as \emph{distributed} when the allocations at any element depend only on
\emph{local} state: the quantity offered by the seller at that element, and the
bids for that element only \cite{lazar}. In this work, the proposed mechanism
allows the distribution of bids, where there are many ISPs each holding
thier own local auction; there is no entity that holds a global market knowledge.

In a PSP mechanism, bids consist of (i) an available (required) quantity and (ii) a unit-price (calculated
using its own demand functions). Buyers submit bids cyclically until an
($\epsilon$-Nash) equilibrium is reached and a local auction is concluded.

(HOW DO WE MODEL ISP REVENUE? FUTURE WORK?)

The form of the auction mechanism presented here is described as a \emph{locally}
pure-strategy progressive game with incomplete, but perfect information.
In a distributed setting, local markets have perfect local information, since you know what each move of the opponent is.
However, since users are not aware of behavior in other auctions, it is a game of incomplete information.
We complete a comprehensive analysis of market dynamics, and will assume
complete and perfect information in order to verify properties and validate
results of the auction mechanism.

(TO ORGANIZE)\\
The main contribution of this work 
is an auction mechanism inspired by the classic PSP throughput problem. In
order to apply a distributed PSP implementation to the CMHK market,
we analize the behavior of users in a dynamical data exchange market. As both buyers and sellers are able
to change their bid strategies, and as each user only has \emph{local}
information about the bidding environment, it is clear that an unconstrained
market, even with a finite number of users, could suffer from the communication
expense from numerous local auctions trading an infinitely divisible resource.
We will assume that the cost of participating in the CMHK secondary market is
absorbed by the bid fee, which could represent data used in submitting bids, or
a fee charged per unit of data, or a flat rate charged at the completion of the
purchase. It is worth mentioning that CMHK users are not allowed to resell data
purchased from the CMHK
market, additionally, the purchased data does not carry to the next
service period. Therefore, a market equilibrium, where
supply equals demand, requires that users maintain incentive for truthfullness
across a distributed setting.
To the best of our knowledge, this is the first work to provide a truthful
mechanism in a distributed setting for data-exchange based on market behavior.
\\
\textbf{Remark:} It is certainly possible to extend the mechanism, alleviating the
restrictions introduced by the CMHK secondary market. We reserve this for
future work.

We claim that the CMHK market is
able to achieve an equilibrium as the sellers and buyers have an
incentive for a collaborative exchange, and as our mechanism provides incentives
for optimal, effective communication between the connected users.

Despite the small message space, with many user types, there is no single
way to do the transformation from the direct revelation mechanism to the
desired one. Our mechanism is designed by guessing
right direct-revelation-to-desired-mechanism transformation and building it
into the allocation rule to be the primary step in the design. This incentive for a user to
truthfully reveal its type is built into the user strategies. As in classic
mechanism design, we determine the equilibria as result of incentive
compatibility in our mechanism design. 
We claim that in the CMHK market our formulation not only holds the desired VCG qualities,
but minimizes comminication overhead 
and auction duration, resulting in a convergence time (FIND COMPETITIVE RATIO?)
with respect to the classic throughput problem.

The strategies described in this paper have removed the
necessity for a user to determine its own valuation function, we intend to show that the market dynamics resulting from the
construction of the user strategy space results in truthful bids that are optimal for all users,
i.e. bid prices are to the marginal value as determined by market dynamics. 
This is the (built-in) transformation from the
direct-revelation mechanism to the desired message space.

The paper is organized as follows...

@@

\subsection{Motivation for Privacy/Security}(NEW SECTION)

A property of PSP is that the user valuations are held private.

1. The seller doesn't update with the ISP, and so does not know the market price
 in the data-exchange market.\\
2. The auction is distributed, so there is no collusion between sellers and
ISP.\\
3. The mechanism is self-contained, and only requires participation. (THINK!)
4. Better economy, as few users will get data plans with a lot of data, make
money, allowing others to have cheaper data plans and not pay a lot for
texting, phone calls (Buzzfeed). Free market capitalism! \\
(CONCERN HERE ABOUT THROTTLING)

@@

@@

@@

@@

We assume that the CMHK market does not have network
bottlenecks, which is purely a bandwidth problem, as in \cite{semret}, and as
bandwidth in wireless networks is not the focus of this paper. We derive a globally optimal strategy suited for
users with local information in a distrubuted data-sharing model.

@@

>>>>

\begin{abstract}
We investigate the 2cm app, a data-exchange platform published for China Mobile Hong
Kong 4G Pro Service Plan customers. Telecommunications ISPs' revenue is typically
gained by charging users a fixed fee for a maximum amount
of data usage in a month, i.e., a monthly data cap \cite{???}. 
2cm's (2nd exchange market) data exchange platform allows users to submit
bids to buy and sell data.
This usage model, is, as far as our knowledge, the first data trading
platform that allows customers to buy and sell their own data. The study of
auction behavior in a data-exchange market distributed over mobile devices is
largely unexplored.
We describe a distributed auction mechanism for data exchange inspired by the
classic PSP throughput problem,
and prove that our distributed data exchange mechanism provides incentive
compatibility (social choice function), and that we have efficiency
using only partial valuation information of each participant in an exchange market.

@@

In this work, we propose \emph{a distributed progressive second price (PSP) auction in
order to maximize social utility in a shared-data market}
A quality of the PSP auction is that
demand information is not known centrally, rather, it is distributed in the
buyers' valuations. The mechanism for an auction is defined
as \emph{distributed} when the allocations at any element depend only on
\emph{local} state: the quantity offered by the seller at that element, and the
bids for that element only \cite{lazar}. In this work, the proposed mechanism
allows the distribution of bids, where there are many auctioneers, each holding
thier own local auction, and there is no single entity holds a global market knowledge.

In a PSP mechanism, bids consist of (i) an available (required) quantity and (ii) a unit-price (calculated
using its own demand functions). Buyers submit bids cyclically until an
($\epsilon$-Nash) equilibrium is reached and a local auction is concluded. 
The form of the auction mechanism presented here is described as a \emph{locally}
pure-strategy progressive game with incomplete, but perfect information.
In the distributed setting, we assume users have a binary type, either seller,
i.e. auctioneer, or buyer. The perspective of strategy changes according to the user
type. We assume unilateral strategies, and so sellers are unable to
derive opponent information from buyer bids, and a buyer recieves updates but
may not be aware of the behavior of opponent strategies in other markets.
We complete a comprehensive analysis of market dynamics, and will assume for
our analysis a game of complete and perfect information in order to verify
properties and validate results of the auction mechanism.

The body of this work describes an evolutionary system that drives an auction
mechanism inspired by the classic PSP throughput problem \cite{lazar}. In
order derive a distributed PSP implementation that arrives at an optimal
objective,
we analyze the behavior of users in a dynamical data exchange market. 
It is known from \emph{Arrow's Theorem}, that in a multi-auction model, no deterministic strategy can
provide a mapping of the preferences of users into a market-wide (complete
and transitive) strategy while also meeting a specified set of criteria:
unrestricted domain, non-dictatorship, Pareto efficiency and independence of
irrelevant alternatives. 
Therfore, as both buyers and sellers are able
to change their bid strategies, and as each user only has \emph{local}
information about the bidding environment, it is clear that a better market
position can only be determined by an adaptive, or evolutionary, strategy.
In other words, a move to a beter market position is synonymous to a
strategic bid. In modern auctions, a strategy must meet a certain set of
criteria: 1) truthfulness as a dominant strategy, 2) individual rationality/
selfishness.  
A Nash market equilibrium, where
supply equals demand, requires that users maintain incentive for truthfulness
across a distributed setting.
As both buyers and sellers are able
to change their bid strategies, and as each user only has \emph{local}
information about the bidding environment, it is clear that an unconstrained
market, even with a finite number of users, could suffer from the
expense of many local auctions trading an infinitely divisible resource.

Using the CMHKs data exhange platform as a host for our distributed strategic
PSP mechanism, we show that in the market of one-time transaction payoffs,
where the exchange is a quantity of cellular data transferred between multiple
users, that there exists a primary $\epsilon$-Nash market equilibrium that is
the winning dominant strategy in the multi-auction system.
To the best of our knowledge, this is the first work to provide a comprehensive
derivation of a truthful mechanism in a distributed setting for
data-resource-exchange based on market behavior. In addition, we are the first
to adapt the PSP mechanism to be contained within a market topology. The market
topology and the user strategy are organically determined by the impact of user
actions, 1) and 2), on market dynamics, and so determines a minimally optimal objective
representing user valuation globally, and so fufills an additional property of
economy over time and space. We further include the ISP as a deaf and blind
user, who nonetheless holds the power to create a monopoly, thereby providing a free
market space in which the market may operate, and real-world implications.

We claim that our mechanism is designed to optimally progress towards an
equilibrium by providing users with an incentive framework, and so rational
users choose a market-collaborative exchage. 
%\textbf{Remark:} It is certainly possible to extend the mechanism, alleviating the
%restrictions introduced by the CMHK secondary market. We reserve this for
%future work.
In classic mechanism design, with multiple user types, there is no single
way to design the transformation from the direct revelation mechanism to its
corresponding computational design. We apply a modifier to the PSP mechanism in
order to mutate the strategy space, following dynamic user
correspendence. As in \cite{lazar}, we take the direct
approach by guessing the right modifier, and context, such that we have the
desired result by composition with the PSP rules. 
As in \cite{lazar}, the incentive for a
user to truthfully reveal its type is built into the user strategies. Then,
local equilibria follow as a result of incentive
compatibility characterizing best strategy moves. \\ 
\textbf{Remark:} The terms ``bid" and ``strategy" are often interchangable,
referencing mechanism design and game theory, respectively.\\
We claim that our formulation not only holds the desired VCG qualities,
but minimizes comminication overhead 
and auction duration, resulting in a convergence time (FIND COMPETITIVE RATIO?)
with respect to the classic throughput problem.

The user strategies are organic in that they are natural, or
induced by the dynamic market itself. Thus, according to second-price strategy,
we have an autonomous, self-updating (NEW WORD) and inclusive optimization, defined in terms of the multi-objective solution.
This is the (built-in) transformation from the
direct-revelation mechanism to the desired message space, (OWN WORDS) where each user
message defines a strategic point, which we may interpret as a move to a better
market position. Then, in the limit of the data-model, a user reveals its
valuation of a quantitiy of data-resource over the whole range of possible demands.

The paper is organized as follows... (TODO)

@@

@@

VCG possible outcomes are characterized by bipartite matchings

@@

We investigate the 2cm app, a data-exchange platform published for China Mobile Hong
Kong 4G Pro Service Plan customers. Telecommunications ISPs' revenue is typically
gained by charging users a fixed fee for a maximum amount
of data usage in a month, i.e., a monthly data cap \cite{???}. 
2cm's (2nd exchange market) data exchange platform allows users to submit
bids to buy and sell data.

@@

\subsection{The Data Market Problem}

We address several topics under discussion in the real-monetary market of virtual
data ownership. The issue of digital property is a well-known debate. The
proliferation of services that are moving from grid to node communication
outdates algorithms designed for optimization in this space. Direct and
network-based communication between mobille devices allows for a simple
mutation of classic optimization models. We will assume that the cost of participating in the CMHK secondary market is
absorbed by the bid fee, which could represent data used in submitting bids, or
a fee charged per unit of data, or a flat rate charged at the completion of the
purchase. Thus, the bid fee acts to limit market iterations. \cite{semret}
provides a proof, where convergence time is inversely related to $\epsilon$.
Our design extends the pricing function:
\begin{itemize}
    \item A mutation characterized by a new variable cost, absorbed into the bid fee,
        represents the
        fact that CMHK users are denied resale and carryover of shared data, effectively creating
        a form of liability with each transaction. 
\end{itemize}
This additonal fee acts as a regulate the mechanism behavior itself, as in a
real-world situation, it is not ideal for fully-connected, asychronous
user-to-user communication, which would obviously thrash the network. The
mutation of the bid fee $\epsilon$ is based on real-world parameters associated
with individual users. This information may be collected from a specific
device's configuration, i.e. enabled roaming, daily data restrictions etc.
We claim that our mechanism is self-regulating, and furthermore, optimized to satisfy the
needs of the individual.

A defining property of PSP is that user valuations are held private. 
The CMHK model provides a unique opportunity for social equilibrium, as it
allows users to share data without sharing the same data plan, a restriction in
most ISPs, such as \cite{att}. We reason that the CMHK secondary-market
approximates local, free-market economy. Laws such as \cite{fedbill} exist to regulate ISPs
as they have historically come close to monopolizing regional markets, leading
to consumer abuse. Our mechanism
takes advantage of the opportunity for full generalization provided by CMHK.
Because CMHK is a generalization of more restrictive ISP practices, it is simple
to adapt our mechanism to the data-sharing
plans published by any ISP, i.e. the family, or corporate, data-sharing plan
\cite{att}.
We argue that data-sharing plans in general may be
biased against the end-user. Adding devices to a shared-data plan includes a
base fee for other services that have relatively small demand in comparison to
the demand for data. Effectively, users must pay for services that go unused in
order to increase the amount of data for a shared plan. Flexible data-sharing
plans are similar to the CMHK market, where a limited number of devices may
share a single data plan. A shared-data plan, however limited, offers better economy
by creating primary users with a service package with a lot of data, and
limited number of secondary users that are only using data \cite{att}.
The CMHK model allows for primary and secondary users to freely correspond,
without the restriction of a static primary-secondary user association.
This effectively creates a competitive secondary market, and contributes to the
dynamics of a free-market economy. Market competition is a desirable quality in
free markets, and is encouraged, particularly in wireless and data services. In
fact, California Legistature has recently passed laws promoting
competition and enforcing fair practice of ISPs \cite{cabill}.

We determine the need for privacy to extend from the users to the data-sharing market, in
order to protect market fairness and exploitation of information by the ISP. In
our model, free-market exchange is protected as privacy is integrated into the
mechanism. Our design extends end-user privacy by the following: 
\begin{itemize}
    \item A mutation of user type, where
    the ISP is represented by the blind, deaf user $\kappa$. Then, 
    sellers do not update pricing information with the ISP, thereby hiding
    its local market price in the data-exchange market. As the ISP has limited
    information from its ``competitor", it is unable to sabatoge prices derived
    from fair market competition.
    \item The mechanism is self-contained, as prices are derived from market
    dynamics, and only requires user participation,
    therefore there cannot be any nefarious or criminal entity influencing
    market dynamics.
\end{itemize}
Thus, we claim that our model supports and protects the secondary market, allowing it
to be in direct competition with its parent ISP, and so contributes to the
regulation of ISPs \cite{fedbill} and supports a regional free-market economy
with respect to wireless data \cite{cabill}.

In the original bandwidth-sharing model, the allocation role defines the active edges in a network for a particular bidder. 
The flexibily of correspondance, and
the ability for instantaneous communication in the distributed wireless network, allows for a more general, and
thus adaptive strategy. We therefore introduce additional restrictions on
defining properties of PSP multi-auctions, and claim they are normal.

@@

We address the market risks and securities in the CMHK secondary market. 
We provide a game-theoretic model of a real market progression, which we use to
derive, then define, adaptive variables. 
We assume that the data-sharing market does not have network
bottlenecks (although congestion is a similar, albeit separate issue), which is purely a bandwidth problem, as in \cite{semret}, and as
bandwidth in wireless networks is not the focus of this paper, we derive a globally optimal strategy suited for
users with local information in a distrubuted data-sharing model.

@@

\bibitem{att}
\textit{AT\&T Mobile Share Flex Plans}
\url{https://www.att.com/plans/wireless/mobile-share-flex.html}
2018

\bibitem{cabill}
\textit{Communications: broadband Internet access service}, S.B. 822. Reg. Sess.
2017-2018. (2018).

\bibitem{fedbill}
\textit{No Rate Regulation of Broadband Internet Access Act},H.R. 2666, 114th
Cong. (2016).
